Studying public transit API query logs\\ to get an indication of travel flows

### 2016-01-06 paper.tex
Review Section 7.

Related work~\cite{verborgh2014lonesome} suggested to add additional metadata in the HTTP headers in order to track the user's intention.
While this is an interesting suggestion, it does not overcome the problem of caching.
In order to create a better representation of travel intentions, future work can gather logs by POST-requests with the only purpose to gather analytics of travel intention.
This is a similar approach than what happens on the Web of Documents today with \emph{Piwik} or \emph{Google Analytics}.

>>>>

Related work~\cite{verborgh2014lonesome} suggested to add additional metadata in the HTTP headers in order to track the user's intention.
While this is an interesting suggestion, it does not overcome the problem of caching.
In order to create a better representation of travel intentions, future work can gather logs by POST requests with the only purpose to gather analytics of travel intention.
This is a similar approach than what happens on the Web of Documents today with \emph{Piwik} or \emph{Google Analytics}.
